\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Hans Elizaga} & Email : \href{mailto:helizaga@berkeley.edu}{helizaga@berkeley.edu}\\
  \href{http://hanselizaga.me/}{http://hanselizaga.me/} & Mobile : 925-212-4633 \\
  \href{https://github.com/helizaga}{https://github.com/helizaga}
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California - Berkeley}{Berkeley, CA}
      {Bachelors of Arts in Data Science and Cognitive Science;  Overall GPA: 3.56}{Graduation: May 2020}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Berkeley Wireless Research Center}{Berkeley, CA}
      {Associate System Administrator}{Oct 2018 - Present}
      \resumeItemListStart
        \resumeItem{Server Monitoring}
          {Use monitoring tools such as Ganglia and Nagios to debug networking issues. Used shell scripting in conjunction with Apache virtual hosts and Puppet modules to automate routine tasks, optimizing system availability (averaging 99.9\% up-time.)}
        \resumeItem{Infrastructure Support}
       	 {Set up user workstations, assisted in troubleshooting system issues in Unix and OSX computing environments, restore databases/privileges, and setup A/V equipment during weekly seminars.}
        \resumeItem{Website Hosting}
          {Responsible for creating, managing, and updating company website content. Migrated website's CMS from Drupal to WordPress.}
         \resumeItem{Storage Management}
         {Perform daily tape backup of required file systems and systems data according to specific settings for security and streamlined data flow.}
      \resumeItemListEnd

    \resumeSubheading
      {Nomsi}{Walnut Creek, CA}
      {Web Developer}{Aug 2018 - Dec 2018}
      \resumeItemListStart
        \resumeItem{Full-Stack}
        {Created a web layout and user interface in HTML and CSS and designed  back-end server code using JavaScript and AJAX libraries.}
        \resumeItem{Q/A Testing}
        {Carried out unit tests, integration tests, and end-to-end tests to discover errors and optimize usability.}
      \resumeItemListEnd

    \resumeSubheading
		{Society of Hispanic Professional Engineers (SHPE)}{Concord, CA}
		{Public Relations Officer}{Aug 2017 - Jul 2018}
		\resumeItemListStart
			\resumeItem{Event Organization}
			{Successfully executing club socials, fundraisers and workshops with other on-campus organizations.}
			\resumeItem{Executive Assistance}
			{Assisted the upper management of SHPE by interacting with executives of STEM companies in the Bay Area}
	\resumeItemListEnd


    \resumeSubheading
      {Northgate High School}{Walnut Creek, CA}
      {Wrestling Coach}{Nov 2017 - Present (Seasonal)} 
      \resumeItemListStart
        \resumeItem{Leadership}
          {Trained students in folkstyle and Olympic wrestling. Monitored individual performances during practice and competition, working on suitable strategies according to each student's wrestling and fitness capabilities. Helped lead team to consecutive league championships and its first district championship.}
      \resumeItemListEnd
      
      
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{To-Do List (Spring 2020)}
      {Developed a to-do list app with Python, Django, HTML, and SQLite}
    \resumeSubItem{Document Scanner (Spring 2020)} 
    {Developed a document scanner using Python and OpenCV.}
    \resumeSubItem{Waste Image Classifier (Fall 2019)}
    {Used convolution neural networks and a pre-trained Inception model to sort random pictures into trash or non-trash classifications.}
    \resumeSubItem{Movie Recommendation System (Spring 2019)}
      {Developed a movie recommended system with collaborative filtering using a k-nearest neighbors algorithm on using Pandas and Python.}
    
     
  \resumeSubHeadingListEnd

%-----------Skills/Awards-----------------
\section{Skills/Award}
	\resumeSubHeadingListStart
		\resumeSubItem{Languages} 
		{Python, C++, HTML, CSS, JavaScript, MySQL}
		\resumeSubItem{Frameworks/Tools}
		{Git, Slack, Pandas, Numpy, SKlearn, Scipy, Matplotlib, Django, TensorFlow}
		\resumeSubItem{Award/Honors}
		{Academic Honors (Summer 2016-Fall 2017, Winter 2018-19, Spring 2019), Consortium of Information Systems Scholarship (2017), Warren L Finke Memorial Scholarship (2017), Bernard Osher Scholarship (2017)}
	\resumeSubHeadingListEnd
	
\end{document}
